Trends of SDR in Thessaloniki

### 2023-07-05 Article.Rmd
Commit 2023-07-05 19:09
Commit 2023-07-05 20:14

We calculated the SDR trends, from the mean daily values of the departure from the seasonal values, for the whole time series for the three sky conditions (Table\ \ref{tab:trendtable}).

@@

panderOptions("table.alignment.default", "center")
pander(LT,
       caption = "\\label{tab:trendtable}Trends of daily SDR means, for different sky conditions. All cases have a statistical significance above $99.9\\%$")
# knitr::kable(LT, caption = "Trends of daily means by sky conditions.")

@@

```{r cumsum, echo = FALSE, fig.cap='two plots', fig.subcap=c('one plot', 'the other one'), out.width='.35\\linewidth', fig.asp=1, fig.ncol = 2}
knitr::include_graphics(c("./images/CumulativeDailyCumSum-1.png", "./images/CumulativeDailyCumSum-9.png"))
```

@@

-------------------------------------------------
                   **END**
-------------------------------------------------

>>>>

We calculated the SDR trends, from the mean daily values of the departure from the seasonal values, for the whole time series for the three sky conditions (Table\ \ref{tab:trendtable}).
In this time period, we could not find any significant break or change in the variability of the trends.
Other studies for the European region are reporting a change of the SDR slope, around the '80, few years before the start of our records [@Wild2021; @Yuan2021; @Ohmura2009].

@@

panderOptions("table.alignment.default", "center")
pander(LT,
       caption = "\\label{tab:trendtable}Trends of daily SDR means, for different sky conditions. All cases have a statistical significance above $99.9\\%$.")
# knitr::kable(LT, caption = "Trends of daily means by sky conditions.")

@@

```{r cumsum, echo = FALSE, fig.cap='two plots', fig.subcap=c('one plot', 'the other one'), out.width='.32\\linewidth', fig.asp=1, fig.ncol = 3}
knitr::include_graphics(c(
    "./images/CumulativeDailyCumSum-1.png",    # ALL sky
    "./images/CumulativeDailyCumSum-5.png",    # CLEAR sky
    "./images/CumulativeDailyCumSum-9.png"))   # Cloud sky
```

@@

-------------------------------------------------
                   **END**
-------------------------------------------------
\newpage
